Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)

### 2015-09-16 research_class/paper.tex
Fix typo: s/describe/described/
Fix wrong-word typo: s/leader/node/

\begin{enumerate}
\item If there is line of text that has been sent but not yet
    added (applied) to the state machine or there are no lines of text
    on the pending send queue, then the function does nothing.
\item A text line is removed from the head of the pending send queue
    and stored in \emph{curSend} to indicate that a send is in
    progress. Then a client request is made using an atomic
    \emph{seqAppend} command to add the new text to the state machine
    (\emph{seqAppend} is describe below).  The \emph{seqAppend}
    operation attempts to append the text line to a list at the
    \emph{history} key in the state machine.
\item When the atomic \emph{seqAppend} operation completes, it may
    have failed (if another text line was appended first), in which
    case the flush function puts the failed text line back on the
    pending send queue. Whether the send was successful or failed, the
    \emph{curSend} variable is set to nil/null to indicate that no
    send is in progress. The next time the flush function runs it will
    attempt to send again. % TODO: reword
\end{enumerate}

@@

In addition, the full chat application was also tested manually by
loading the initial chat application landing page to create a Raft
over WebRTC cluster with a single leader acting as leader. Then lines
of text were entered into the text area each followed by clicking the
Send button. Figure~\ref{fig:browser_chat_1} shows a screenshot of the
browser after the first node/tab of the chat application is created
and a line of text was sent:

>>>>

\begin{enumerate}
\item If there is line of text that has been sent but not yet
    added (applied) to the state machine or there are no lines of text
    on the pending send queue, then the function does nothing.
\item A text line is removed from the head of the pending send queue
    and stored in \emph{curSend} to indicate that a send is in
    progress. Then a client request is made using an atomic
    \emph{seqAppend} command to add the new text to the state machine
    (\emph{seqAppend} is described below).  The \emph{seqAppend}
    operation attempts to append the text line to a list at the
    \emph{history} key in the state machine.
\item When the atomic \emph{seqAppend} operation completes, it may
    have failed (if another text line was appended first), in which
    case the flush function puts the failed text line back on the
    pending send queue. Whether the send was successful or failed, the
    \emph{curSend} variable is set to nil/null to indicate that no
    send is in progress. The next time the flush function runs it will
    attempt to send again. % TODO: reword
\end{enumerate}

@@

In addition, the full chat application was also tested manually by
loading the initial chat application landing page to create a Raft
over WebRTC cluster with a single node acting as leader. Then lines
of text were entered into the text area each followed by clicking the
Send button. Figure~\ref{fig:browser_chat_1} shows a screenshot of the
browser after the first node/tab of the chat application is created
and a line of text was sent:
